Visualizations for the manuscript

### 2022-04-01 metanalysis_visualization/manuscript_Figures.Rmd
ITS sex implementation

```{r}
outputDir <- "../../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

@@

bootstrapping_slopes <- function(df, 
                                 bootstrap_size, 
                                 count = "count_icd", 
                                 percentage = "percentage", 
                                 group_name = .y) {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = df[[count]],
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- df$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>% 
    mutate(group = group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration") %>% 
    mutate(group = group_name)
  return(list(bootstrapped_coefficients_df, 
              bootstrapped_fitted_df))
}
```

@@

bootstrapped <- count_icd_all_boot %>%
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(count_icd_all_boot$siteid)

bootstrapped_coefficients_all <- lapply(bootstrapped, `[[`, 1) %>% bind_rows(.id = "siteid")
bootstrapped_fitted_all <- lapply(bootstrapped, `[[`, 2) %>% bind_rows(.id = "siteid")
```

@@

```{r}
### Feb 19-April 21
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>%
  left_join( country_map )

@@

```{r Interrupted time series by sex}

  # pivot_wider(names_from =  sex, values_from = c(count, percentage))
  # group_by(siteid) %>% # necessary to generate time correctly 
  # rename(count_psy_patients = count_psy, 
  #        percentage = percentage_psy) %>% 
  # mutate(count_no_psy_patients = count_icd - count_psy_patients, 
  #        month_year = format(time_p, "%m"),
  #        time = seq_along(time_p))

bootstrap_size = 10

@@

bootstrapped_sex <- patients_hospitalized_agg_sex_perc_all %>%
  group_by(siteid, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size, count = "count"))
names(bootstrapped_sex) <- unique(patients_hospitalized_agg_sex_perc_all$siteid)

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>% bind_rows(.id = "siteid")
bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows(.id = "siteid")

quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

@@

```{r}
names_site_id <- unique(df_coefficients_boot_sex$siteid)

plot_annotations <- df_coefficients_boot_sex %>% 
  group_by(siteid, sex) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)
```

>>>>

```{r}
outputDir <- "../../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = "../public-data/country_mapping.txt")
```

@@

bootstrapping_slopes <- function(df,
                                 group_name,
                                 bootstrap_size,
                                 count = "count_icd",
                                 percentage = "percentage") {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = df[[count]],
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- df$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>%
    bind_cols(group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                            .id = "iteration") %>%
    bind_cols(group_name)
  return(list(bootstrapped_coefficients_df,
              bootstrapped_fitted_df))
}
```

@@

bootstrapped <- count_icd_all_boot %>%
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, group_name = .y, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(count_icd_all_boot$siteid)

bootstrapped_coefficients_all <- lapply(bootstrapped, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_all <- lapply(bootstrapped, `[[`, 2) %>% bind_rows()
```

@@

```{r}
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>%
  left_join( country_map )

@@

```{r Interrupted time series by sex}
bootstrap_size = 10

@@

bootstrapped_sex <- patients_hospitalized_agg_sex_perc_all %>%
  group_by(siteid, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map( ~bootstrapping_slopes(.x, group_name = .y, bootstrap_size = bootstrap_size, count = "count"))

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows()
```

```{r Interrupted time series by sex}
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, period, siteid, sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

@@

```{r}
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
```

```{r}
# expand.grid(
#   unique(df_coefficients_boot_sex$siteid),
#   unique(df_coefficients_boot_sex$sex)
# ) %>% 
#   t() %>% 
#   paste(unique(.$siteid),
#         unique(.$sex), 
#         collapse = " "
#   )
# 
# names_plot_annotations_sex <- c()
# for (site in unique(df_coefficients_boot_sex$siteid)) {
#   for (sex in unique(df_coefficients_boot_sex$sex)) {
#     names_plot_annotations_sex <- c(names_plot_annotations_sex, paste(site, sex))
#   }
# }

# plot_annotations_sex <- df_coefficients_boot_sex %>% 
#   group_by(siteid, sex) %>% 
#   group_map( annotation_function ) %>% 
#   set_names(names_site_id) %>% 
#   unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  # label = plot_annotations
)
```
